Assessing the impacts of time to detection distribution assumptions on detection probability estimation

### 2017-04-03 Supplement.tex
Updates to draft and reviewer's comments.

>>>>

\begin{table}[ht]
\footnotesize\centering
\begin{tabular}{l|l|l|l|cccc|cccc}
 \multicolumn{4}{c|}{ } & \multicolumn{4}{c|}{\underline{Non-mixture model}} & \multicolumn{4}{c}{\underline{Mixture model}} \\
 \multicolumn{4}{c|}{ } & Med $p$ & Q($p$) & 50\% & 90\% & Med $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
  \hline
 \parbox[t]{2mm}{\multirow{14}{*}{\rotatebox[origin=c]{90}{TTDD used to simulate data}}} & \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Non-mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.67 & 0.84 & 0.11 & 0.94 & 0.76 & 0.92 & 0.00 & 0.70 \\ 
   &  &  & Lognormal & 0.54 & 0.60 & 0.81 & 1.00 & 0.68 & 0.88 & 0.05 & 0.79 \\ 
   &  &  & Weibull & 0.55 & 0.61 & 0.79 & 0.99 & 0.69 & 0.84 & 0.16 & 0.87 \\ 
  \cline{3-12}
 & & &  Exponential & 0.49 & 0.45 & 0.51 & 0.93 & 0.45 & 0.30 & 0.47 & 0.86 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.48 & 0.46 & 0.57 & 0.90 & 0.57 & 0.72 & 0.42 & 0.85 \\ 
   &  &  & Lognormal & 0.49 & 0.45 & 0.53 & 0.93 & 0.54 & 0.69 & 0.37 & 0.89 \\ 
   &  &  & Weibull & 0.48 & 0.48 & 0.40 & 0.91 & 0.59 & 0.74 & 0.37 & 0.80 \\ 
  \cline{2-12}
& \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.62 & 0.76 & 0.42 & 0.99 & 0.71 & 0.86 & 0.10 & 0.89 \\ 
   &  &  & Lognormal & 0.50 & 0.47 & 0.95 & 1.00 & 0.64 & 0.84 & 0.09 & 0.97 \\ 
   &  &  & Weibull & 0.50 & 0.47 & 0.92 & 1.00 & 0.64 & 0.77 & 0.39 & 0.98 \\ 
  \cline{3-12}
 & & &   Exponential & 0.88 & 1.00 & 0.00 & 0.00 & 0.50 & 0.49 & 0.54 & 0.95 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.24 & 0.01 & 0.00 & 0.00 & 0.52 & 0.53 & 0.76 & 0.99 \\ 
   &  &  & Lognormal & 0.18 & 0.00 & 0.00 & 0.00 & 0.49 & 0.47 & 0.66 & 0.97 \\ 
   &  &  & Weibull & 0.18 & 0.00 & 0.00 & 0.00 & 0.52 & 0.52 & 0.80 & 1.00 \\ 
   \hline
\end{tabular}
\caption{Summary of mixture vs. non-mixture model fits when the detection probability is $\pdet =0.50$.  
In all cases, the inference model family matches the dataset family.  
Med $p$: average across simulations of the posterior median of $\pdet$.  
Q($p$): average proportion of the posterior distribution of $\pdet$ that is larger than the true value.  
50\% and 90\% coverage is expressed as the proportion of 100 simulations for which the true value of $\pdet$ lies within the appropriate credible interval.}

\vspace{1.2cm}

\begin{tabular}{l|l|l|l|cccc|cccc}
 \multicolumn{4}{c|}{ } & \multicolumn{4}{c|}{\underline{Non-mixture model}} & \multicolumn{4}{c}{\underline{Mixture model}} \\
 \multicolumn{4}{c|}{ } & Med $p$ & Q($p$) & 50\% & 90\% & Med $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
  \hline
 \parbox[t]{2mm}{\multirow{14}{*}{\rotatebox[origin=c]{90}{TTDD used to simulate data}}} & \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Non-mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}}& Gamma & 0.69 & 0.59 & 0.78 & 0.98 & 0.78 & 0.79 & 0.35 & 0.90 \\ 
   &  &  & Lognormal & 0.59 & 0.31 & 0.45 & 0.91 & 0.73 & 0.69 & 0.63 & 0.90 \\ 
   &  &  & Weibull & 0.60 & 0.38 & 0.59 & 0.99 & 0.73 & 0.68 & 0.59 & 0.94 \\
  \cline{3-12}
   &  &  & Exponential & 0.64 & 0.47 & 0.50 & 0.85 & 0.61 & 0.29 & 0.33 & 0.82 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}}& Gamma & 0.64 & 0.44 & 0.46 & 0.89 & 0.68 & 0.66 & 0.51 & 0.85 \\ 
   &  &  & Lognormal & 0.64 & 0.47 & 0.36 & 0.87 & 0.67 & 0.63 & 0.44 & 0.79 \\ 
   &  &  & Weibull & 0.61 & 0.40 & 0.46 & 0.88 & 0.69 & 0.67 & 0.46 & 0.88 \\ 
  \cline{2-12}
& \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}}& Gamma & 0.60 & 0.36 & 0.78 & 1.00 & 0.71 & 0.63 & 0.81 & 0.99 \\ 
   &  &  & Lognormal & 0.52 & 0.13 & 0.12 & 0.74 & 0.67 & 0.54 & 0.93 & 1.00 \\ 
   &  &  & Weibull & 0.51 & 0.17 & 0.23 & 0.82 & 0.66 & 0.52 & 0.92 & 1.00 \\ 
  \cline{3-12}
   &  &  & Exponential & 0.93 & 1.00 & 0.00 & 0.00 & 0.63 & 0.46 & 0.45 & 0.87 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.26 & 0.00 & 0.00 & 0.00 & 0.58 & 0.34 & 0.51 & 0.95 \\ 
   &  &  & Lognormal & 0.20 & 0.00 & 0.00 & 0.00 & 0.61 & 0.41 & 0.58 & 0.92 \\ 
   &  &  & Weibull & 0.19 & 0.00 & 0.00 & 0.00 & 0.56 & 0.34 & 0.44 & 0.95 \\ 
   \hline
\end{tabular}
\caption{Summary of mixture vs. non-mixture model fits when the detection probability is $\pdet =0.65$.  
In all cases, the inference model family matches the dataset family.  
Med $p$: average across simulations of the posterior median of $\pdet$.  
Q($p$): average proportion of the posterior distribution of $\pdet$ that is larger than the true value.  
50\% and 90\% coverage is expressed as the proportion of 100 simulations for which the true value of $\pdet$ lies within the appropriate credible interval.}

\end{table}

\begin{table}[ht]\centering\footnotesize
\begin{tabular}{l|l|l|l|cccc|cccc}
 \multicolumn{4}{c|}{ } & \multicolumn{4}{c|}{\underline{Non-mixture model}} & \multicolumn{4}{c}{\underline{Mixture model}} \\
 \multicolumn{4}{c|}{ } & Med $p$ & Q($p$) & 50\% & 90\% & Med $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
  \hline
 \parbox[t]{2mm}{\multirow{14}{*}{\rotatebox[origin=c]{90}{TTDD used to simulate data}}} & \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Non-mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.75 & 0.39 & 0.45 & 0.92 & 0.83 & 0.62 & 0.55 & 0.91 \\ 
   &  &  & Lognormal & 0.71 & 0.29 & 0.29 & 0.82 & 0.82 & 0.61 & 0.63 & 0.91 \\ 
   &  &  & Weibull & 0.72 & 0.34 & 0.41 & 0.86 & 0.82 & 0.60 & 0.59 & 0.93 \\ 
  \cline{3-12}
    &  &  & Exponential & 0.80 & 0.49 & 0.54 & 0.88 & 0.78 & 0.32 & 0.48 & 0.86 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.79 & 0.44 & 0.45 & 0.87 & 0.81 & 0.59 & 0.45 & 0.90 \\ 
   &  &  & Lognormal & 0.80 & 0.48 & 0.52 & 0.95 & 0.81 & 0.60 & 0.53 & 0.92 \\ 
   &  &  & Weibull & 0.78 & 0.37 & 0.38 & 0.84 & 0.81 & 0.57 & 0.49 & 0.92 \\ 
  \cline{2-12}
& \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.64 & 0.11 & 0.11 & 0.59 & 0.75 & 0.38 & 0.64 & 1.00 \\ 
   &  &  & Lognormal & 0.58 & 0.06 & 0.04 & 0.27 & 0.74 & 0.33 & 0.51 & 0.98 \\ 
   &  &  & Weibull & 0.54 & 0.04 & 0.01 & 0.23 & 0.70 & 0.27 & 0.46 & 1.00 \\ 
  \cline{3-12}
   &  &  & Exponential & 0.96 & 1.00 & 0.00 & 0.00 & 0.78 & 0.45 & 0.42 & 0.86 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.28 & 0.00 & 0.00 & 0.00 & 0.72 & 0.30 & 0.40 & 0.80 \\ 
   &  &  & Lognormal & 0.22 & 0.00 & 0.00 & 0.00 & 0.78 & 0.45 & 0.46 & 0.87 \\ 
   &  &  & Weibull & 0.22 & 0.00 & 0.00 & 0.00 & 0.69 & 0.29 & 0.33 & 0.88 \\ 
   \hline
\end{tabular}
\caption{Summary of mixture vs. non-mixture model fits when the detection probability is $\pdet =0.80$.  
In all cases, the inference model family matches the dataset family.  
Med $p$: average across simulations of the posterior median of $\pdet$.  
Q($p$): average proportion of the posterior distribution of $\pdet$ that is larger than the true value.  
50\% and 90\% coverage is expressed as the proportion of 100 simulations for which the true value of $\pdet$ lies within the appropriate credible interval.}

\vspace{1.2cm}
% Note: both tables are in the same 'table' environment.

\begin{tabular}{l|l|l|l|cccc|cccc}
 \multicolumn{4}{c|}{ } & \multicolumn{4}{c|}{\underline{Non-mixture model}} & \multicolumn{4}{c}{\underline{Mixture model}} \\
 \multicolumn{4}{c|}{ } & Med $p$ & Q($p$) & 50\% & 90\% & Med $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
  \hline
 \parbox[t]{2mm}{\multirow{14}{*}{\rotatebox[origin=c]{90}{TTDD used to simulate data}}} & \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Non-mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.95 & 0.44 & 0.59 & 0.95 & 0.96 & 0.62 & 0.61 & 0.96 \\ 
   &  &  & Lognormal & 0.94 & 0.42 & 0.47 & 0.87 & 0.96 & 0.65 & 0.44 & 0.90 \\ 
   &  &  & Weibull & 0.94 & 0.46 & 0.43 & 0.90 & 0.96 & 0.67 & 0.52 & 0.84 \\ 
  \cline{3-12}
   &  &  & Exponential & 0.95 & 0.54 & 0.48 & 0.90 & 0.94 & 0.37 & 0.42 & 0.89 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.95 & 0.43 & 0.44 & 0.89 & 0.95 & 0.50 & 0.40 & 0.88 \\ 
   &  &  & Lognormal & 0.95 & 0.50 & 0.44 & 0.88 & 0.95 & 0.54 & 0.44 & 0.88 \\ 
   &  &  & Weibull & 0.95 & 0.53 & 0.49 & 0.91 & 0.96 & 0.65 & 0.42 & 0.85 \\ 
  \cline{2-12}
& \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.85 & 0.04 & 0.03 & 0.22 & 0.91 & 0.25 & 0.31 & 0.77 \\ 
   &  &  & Lognormal & 0.85 & 0.03 & 0.03 & 0.16 & 0.92 & 0.28 & 0.38 & 0.86 \\ 
   &  &  & Weibull & 0.71 & 0.01 & 0.01 & 0.02 & 0.87 & 0.22 & 0.28 & 0.68 \\ 
  \cline{3-12}
   &  &  & Exponential & 0.99 & 1.00 & 0.00 & 0.00 & 0.94 & 0.41 & 0.51 & 0.85 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.37 & 0.00 & 0.00 & 0.00 & 0.94 & 0.39 & 0.41 & 0.83 \\ 
   &  &  & Lognormal & 0.27 & 0.00 & 0.00 & 0.00 & 0.94 & 0.40 & 0.43 & 0.83 \\ 
   &  &  & Weibull & 0.28 & 0.00 & 0.00 & 0.00 & 0.93 & 0.36 & 0.47 & 0.80 \\ 
   \hline
\end{tabular}
\caption{Summary of mixture vs. non-mixture model fits when the detection probability is $\pdet =0.95$.  
In all cases, the inference model family matches the dataset family.  
Med $p$: average across simulations of the posterior median of $\pdet$.  
Q($p$): average proportion of the posterior distribution of $\pdet$ that is larger than the true value.  
50\% and 90\% coverage is expressed as the proportion of 100 simulations for which the true value of $\pdet$ lies within the appropriate credible interval.}
\end{table}

\begin{table}[ht]\centering\footnotesize
\centering
\begin{tabular}{l|l|l|cccc|cccc}
 \multicolumn{3}{c}{ } & \multicolumn{4}{c}{\underline{Exponential mixture model}} & \multicolumn{4}{c}{\underline{Gamma mixture model}} \\
 \multicolumn{3}{c}{ } & Med $p$ & Q($p$) & 50\% & 90\%  & Med $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
\parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Data Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.84 & 0.99 & 0.00 & 0.05 & 0.71 & 0.86 & 0.10 & 0.89 \\ 
   &  & Lognormal & 0.89 & 1.00 & 0.00 & 0.00 & 0.78 & 0.93 & 0.01 & 0.56 \\ 
   &  & Weibull & 0.86 & 1.00 & 0.00 & 0.02 & 0.73 & 0.89 & 0.03 & 0.82 \\ 
\cline{2-11}
   &  & Exponential & 0.50 & 0.49 & 0.54 & 0.95 & 0.54 & 0.57 & 0.84 & 1.00 \\ 
\cline{2-11}
& \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.31 & 0.06 & 0.05 & 0.32 & 0.52 & 0.53 & 0.76 & 0.99 \\ 
   &  & Lognormal & 0.26 & 0.02 & 0.00 & 0.09 & 0.59 & 0.68 & 0.52 & 0.91 \\ 
   &  & Weibull & 0.30 & 0.05 & 0.05 & 0.28 & 0.49 & 0.46 & 0.75 & 1.00 \\ 
   \hline
\end{tabular}
\vspace{0.5cm}\\
\begin{tabular}{l|l|l|cccc|cccc}
 \multicolumn{3}{c}{ } & \multicolumn{4}{c}{\underline{Lognormal mixture model}} & \multicolumn{4}{c}{\underline{Weibull mixture model}} \\
 \multicolumn{3}{c}{ } & Med $p$ & Q($p$) & 50\% & 90\% & Med $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
\parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Data Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.63 & 0.80 & 0.23 & 0.99 & 0.63 & 0.74 & 0.54 & 0.98 \\ 
   &  & Lognormal & 0.64 & 0.84 & 0.09 & 0.97 & 0.68 & 0.83 & 0.21 & 0.95 \\ 
   &  & Weibull & 0.63 & 0.81 & 0.18 & 0.99 & 0.64 & 0.77 & 0.39 & 0.98 \\ 
\cline{2-11}
   &  & Exponential & 0.49 & 0.45 & 0.77 & 1.00 & 0.54 & 0.56 & 0.87 & 0.99 \\ 
\cline{2-11}
& \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.45 & 0.36 & 0.60 & 1.00 & 0.55 & 0.58 & 0.77 & 0.98 \\ 
   &  & Lognormal & 0.49 & 0.47 & 0.66 & 0.97 & 0.64 & 0.75 & 0.43 & 0.87 \\ 
   &  & Weibull & 0.43 & 0.30 & 0.51 & 0.97 & 0.52 & 0.52 & 0.80 & 1.00 \\ 
   \hline
\end{tabular}
\caption{Summary of models fits across family of TTDD when true detection probability is $\pdet = 0.50$.
All data and inference models have mixture components.
Med $p$: average across simulations of the posterior median of $\pdet$.  
Q($p$): average proportion of the posterior distribution of $\pdet$ that is larger than the true value.  
50\% and 90\% coverage is expressed as the proportion of simulations for which the true value of $\pdet$ lies within the appropriate credible interval.}

\vspace{0.5cm}
% Note: both tables are in the same 'table' environment.

\begin{tabular}{l|l|l|cccc|cccc}
 \multicolumn{3}{c}{ } & \multicolumn{4}{c}{\underline{Exponential mixture model}} & \multicolumn{4}{c}{\underline{Gamma mixture model}} \\
 \multicolumn{3}{c}{ } & Med $p$ & Q($p$) & 50\% & 90\%  & Med $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
\parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Data Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.83 & 0.96 & 0.04 & 0.21 & 0.71 & 0.63 & 0.81 & 0.99 \\ 
   &  & Lognormal & 0.91 & 1.00 & 0.00 & 0.00 & 0.82 & 0.86 & 0.19 & 0.70 \\ 
   &  & Weibull & 0.87 & 0.98 & 0.01 & 0.09 & 0.75 & 0.72 & 0.54 & 0.97 \\ 
\cline{2-11}
   &  & Exponential & 0.63 & 0.46 & 0.45 & 0.87 & 0.60 & 0.38 & 0.70 & 1.00 \\ 
\cline{2-11}
& \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.33 & 0.01 & 0.02 & 0.05 & 0.58 & 0.34 & 0.51 & 0.95 \\ 
   &  & Lognormal & 0.30 & 0.00 & 0.00 & 0.00 & 0.71 & 0.68 & 0.48 & 0.88 \\ 
   &  & Weibull & 0.32 & 0.00 & 0.00 & 0.00 & 0.53 & 0.25 & 0.31 & 0.89 \\ 
   \hline
\end{tabular}
\vspace{0.5cm}\\
\begin{tabular}{l|l|l|cccc|cccc}
 \multicolumn{3}{c}{ } & \multicolumn{4}{c}{\underline{Lognormal mixture model}} & \multicolumn{4}{c}{\underline{Weibull mixture model}} \\
 \multicolumn{3}{c}{ } & Med $p$ & Q($p$) & 50\% & 90\% & Med $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
\parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Data Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.63 & 0.43 & 0.87 & 1.00 & 0.63 & 0.45 & 0.94 & 1.00 \\ 
   &  & Lognormal & 0.67 & 0.54 & 0.93 & 1.00 & 0.73 & 0.66 & 0.68 & 0.98 \\ 
   &  & Weibull & 0.64 & 0.46 & 0.97 & 1.00 & 0.66 & 0.52 & 0.92 & 1.00 \\ 
\cline{2-11}
   &  & Exponential & 0.55 & 0.24 & 0.39 & 0.95 & 0.58 & 0.36 & 0.69 & 1.00 \\ 
\cline{2-11}
& \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.50 & 0.16 & 0.21 & 0.65 & 0.62 & 0.44 & 0.59 & 0.98 \\ 
   &  & Lognormal & 0.61 & 0.41 & 0.58 & 0.92 & 0.77 & 0.79 & 0.34 & 0.78 \\ 
   &  & Weibull & 0.47 & 0.11 & 0.13 & 0.48 & 0.56 & 0.34 & 0.44 & 0.95 \\ 
   \hline
\end{tabular}
\caption{Summary of models fits across family of TTDD when true detection probability is $\pdet = 0.65$.
All data and inference models have mixture components.
Med $p$: average across simulations of the posterior median of $\pdet$.  
Q($p$): average proportion of the posterior distribution of $\pdet$ that is larger than the true value.  
50\% and 90\% coverage is expressed as the proportion of simulations for which the true value of $\pdet$ lies within the appropriate credible interval.}
\label{tbl:sim2}
\end{table}

\begin{table}[ht]
\footnotesize\centering
\begin{tabular}{l|l|l|cccc|cccc}
 \multicolumn{3}{c}{ } & \multicolumn{4}{c}{\underline{Exponential mixture model}} & \multicolumn{4}{c}{\underline{Gamma mixture model}} \\
 \multicolumn{3}{c}{ } & Med $p$ & Q($p$) & 50\% & 90\%  & Med $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
\parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Data Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.86 & 0.83 & 0.25 & 0.59 & 0.75 & 0.38 & 0.64 & 1.00 \\ 
   &  & Lognormal & 0.93 & 1.00 & 0.00 & 0.01 & 0.88 & 0.80 & 0.33 & 0.72 \\ 
   &  & Weibull & 0.89 & 0.93 & 0.11 & 0.36 & 0.79 & 0.49 & 0.66 & 0.99 \\ 
\cline{2-11}
   &  & Exponential & 0.78 & 0.45 & 0.42 & 0.86 & 0.70 & 0.25 & 0.32 & 0.91 \\ 
\cline{2-11}
& \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.37 & 0.00 & 0.00 & 0.00 & 0.72 & 0.30 & 0.40 & 0.80 \\ 
   &  & Lognormal & 0.34 & 0.00 & 0.00 & 0.00 & 0.85 & 0.77 & 0.24 & 0.65 \\ 
   &  & Weibull & 0.38 & 0.00 & 0.00 & 0.00 & 0.65 & 0.16 & 0.22 & 0.54 \\ 
   \hline
\end{tabular}
\vspace{0.5cm}\\
\begin{tabular}{l|l|l|cccc|cccc}
 \multicolumn{3}{c}{ } & \multicolumn{4}{c}{\underline{Lognormal mixture model}} & \multicolumn{4}{c}{\underline{Weibull mixture model}} \\
 \multicolumn{3}{c}{ } & Med $p$ & Q($p$) & 50\% & 90\% & Med $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
\parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Data Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.65 & 0.16 & 0.16 & 0.85 & 0.67 & 0.23 & 0.34 & 0.99 \\ 
   &  & Lognormal & 0.74 & 0.33 & 0.51 & 0.98 & 0.81 & 0.55 & 0.59 & 0.97 \\ 
   &  & Weibull & 0.66 & 0.17 & 0.22 & 0.87 & 0.70 & 0.27 & 0.46 & 1.00 \\ 
\cline{2-11}
   &  & Exponential & 0.61 & 0.11 & 0.12 & 0.52 & 0.64 & 0.21 & 0.24 & 0.85 \\ 
\cline{2-11}
& \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.64 & 0.09 & 0.10 & 0.41 & 0.77 & 0.49 & 0.46 & 0.93 \\ 
   &  & Lognormal & 0.78 & 0.45 & 0.46 & 0.87 & 0.90 & 0.90 & 0.13 & 0.40 \\ 
   &  & Weibull & 0.57 & 0.04 & 0.02 & 0.19 & 0.69 & 0.29 & 0.33 & 0.88 \\ 
   \hline
\end{tabular}
\caption{Summary of models fits across family of TTDD when true detection probability is $\pdet = 0.80$.
All data and inference models have mixture components.
Med $p$: average across simulations of the posterior median of $\pdet$.  
Q($p$): average proportion of the posterior distribution of $\pdet$ that is larger than the true value.  
50\% and 90\% coverage is expressed as the proportion of simulations for which the true value of $\pdet$ lies within the appropriate credible interval.}
\label{tbl:sim2}

\vspace{0.5cm}

\begin{tabular}{l|l|l|cccc|cccc}
 \multicolumn{3}{c}{ } & \multicolumn{4}{c}{\underline{Exponential mixture model}} & \multicolumn{4}{c}{\underline{Gamma mixture model}} \\
 \multicolumn{3}{c}{ } & Med $p$ & Q($p$) & 50\% & 90\%  & Med $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
\parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Data Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.94 & 0.30 & 0.38 & 0.83 & 0.91 & 0.25 & 0.31 & 0.77 \\ 
   &  & Lognormal & 0.97 & 0.91 & 0.07 & 0.44 & 0.96 & 0.72 & 0.46 & 0.82 \\ 
   &  & Weibull & 0.94 & 0.29 & 0.37 & 0.76 & 0.91 & 0.25 & 0.32 & 0.76 \\ 
\cline{2-11}
   &  & Exponential & 0.94 & 0.41 & 0.51 & 0.85 & 0.92 & 0.26 & 0.33 & 0.82 \\ 
\cline{2-11}
& \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.55 & 0.00 & 0.00 & 0.00 & 0.94 & 0.39 & 0.41 & 0.83 \\ 
   &  & Lognormal & 0.47 & 0.00 & 0.00 & 0.00 & 0.97 & 0.80 & 0.27 & 0.65 \\ 
   &  & Weibull & 0.57 & 0.00 & 0.00 & 0.00 & 0.89 & 0.08 & 0.09 & 0.43 \\ 
   \hline
\end{tabular}
\vspace{0.5cm}\\
\begin{tabular}{l|l|l|cccc|cccc}
 \multicolumn{3}{c}{ } & \multicolumn{4}{c}{\underline{Lognormal mixture model}} & \multicolumn{4}{c}{\underline{Weibull mixture model}} \\
 \multicolumn{3}{c}{ } & Med $p$ & Q($p$) & 50\% & 90\% & Med $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
\parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Data Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.81 & 0.11 & 0.10 & 0.35 & 0.87 & 0.23 & 0.22 & 0.68 \\ 
   &  & Lognormal & 0.92 & 0.28 & 0.38 & 0.86 & 0.95 & 0.55 & 0.57 & 0.92 \\ 
   &  & Weibull & 0.82 & 0.10 & 0.15 & 0.34 & 0.87 & 0.22 & 0.28 & 0.68 \\ 
\cline{2-11}
   &  & Exponential & 0.82 & 0.09 & 0.09 & 0.38 & 0.88 & 0.20 & 0.25 & 0.65 \\ 
\cline{2-11}
& \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}}  & Gamma & 0.91 & 0.09 & 0.10 & 0.42 & 0.97 & 0.79 & 0.26 & 0.63 \\ 
   &  & Lognormal & 0.94 & 0.40 & 0.43 & 0.83 & 0.98 & 0.98 & 0.01 & 0.12 \\ 
   &  & Weibull & 0.84 & 0.01 & 0.00 & 0.03 & 0.93 & 0.36 & 0.47 & 0.80 \\ 
   \hline
\end{tabular}
\caption{Summary of models fits across family of TTDD when true detection probability is $\pdet = 0.95$.
All data and inference models have mixture components.
Med $p$: average across simulations of the posterior median of $\pdet$.  
Q($p$): average proportion of the posterior distribution of $\pdet$ that is larger than the true value.  
50\% and 90\% coverage is expressed as the proportion of simulations for which the true value of $\pdet$ lies within the appropriate credible interval.}
\end{table}
